Models of lens candidates from Space Warps CFHTLS

### 2017-03-01 parts/app.tex
very last bugfixes

\begin{figure}
  \includegraphics[width=\linewidth]{img/rE_comp/rE_comp.png}
  \caption{
    Comparison of Einstein radii \ER obtained from mass tiles directly to those obtained from a parameterized model to test the performance of the conversion algorythm.
    The parameterized model was generated using princible componant analysis on the ensemble of models.
    The blue dashed line represents a perfect recovery of \ER.
    }
  \label{fig:parameter}
\end{figure}

>>>>

\begin{figure}
  \includegraphics[width=\linewidth]{img/rE_comp/rE_comp.png}
  \caption{
    Comparison of Einstein radii \ER obtained from mass tiles directly to those obtained from a parameterized model to test the performance of the parametrisation algorythm.
    The parameterized model was generated using princible componant analysis on the ensemble of models.
    The blue dashed line represents a perfect recovery of \ER.
    }
  \label{fig:parameter}
\end{figure}
